Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-22 src/tex/ms.tex
Added alternative hierarchical modeling results
edits to table caption

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}.
\begin{table}
    \caption{Events that best constrain $\kappa$, where $\tilde{\kappa}$ is the posterior median of $\kappa$.} 
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

@@

\begin{table}
    \caption{Events that show bimodality in the $\kappa$ posterior, where the total mass of the binary is given in solar masses.}
    \begin{ruledtabular}
        \variable{output/bimodal_events_mass.txt}
    \end{ruledtabular}
    \label{tab:bimodal_events_mass}
\end{table}
We understand this effect to be a consequence of the narrow sets of frequencies that are visible for these heavy events, as we mentioned in Sec.~\ref{sec:inclination} and further demonstrate below.

@@

>>>>

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}.
\begin{table}
    \caption{Events that best constrain $\kappa$. \mi{THOMAS: please just use $\kappa$, no need for the $\tilde{\kappa}$ notation}}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

@@

\begin{table}
    \caption{Events that show bimodality in the $\kappa$ posterior tend to have high total masses.}
    \begin{ruledtabular}
        \variable{output/bimodal_events_mass.txt}
    \end{ruledtabular}
    \label{tab:bimodal_events_mass}
\end{table}
We understand this effect to be a consequence of the narrow sets of frequencies that are visible for these heavy events, as we mentioned in Sec.~\ref{sec:inclination} and further demonstrate below.

@@

\section{Alternative results for Bayesian hierarchical modeling}
\label{sec:alternative_results}

\begin{figure}
    \script{corner_Gaussian_appendix_1.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian_appendix_1.pdf}
    \caption{
        Kept all events.
        % The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
        % 2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        % The orange line represents the median of $\mu$ and $\sigma$.
        % The plot shows that the population constraint on $\kappa$ is consistent with GR.
    }
    \label{fig:corner_Gaussian_appendix_1}
\end{figure}

\begin{figure}
    \script{corner_Gaussian_appendix_2.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian_appendix_2.pdf}
    \caption{
        Excluded GW170818 and GW200129.
        % The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
        % 2D contour plot shows $39.35\%$ and $90\%$ confidence level.
        % The orange line represents the median of $\mu$ and $\sigma$.
        % The plot shows that the population constraint on $\kappa$ is consistent with GR.
    }
    \label{fig:corner_Gaussian_appendix_2}
\end{figure}
